\pisodm: Building SOC Applications in the Presence of Non-Functional Requirements

### 2016-04-08 JournalPISODM2016/main.tex
Version for the new journal - same article as RITA

\documentclass{RITA}
\usepackage[T1]{fontenc}
%\usepackage[latin1]{inputenc}
\usepackage[english]{babel}

% Our packages and definitions
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{paralist} % for compact lists: compactitem, compactenum, compactdesc
\usepackage{lipsum}  % for the example environment
\usepackage{amssymb} % for the \blacksquare symbol
\usepackage{subfigure}

\newcounter{examplecounter}
\newenvironment{example}{%\begin{quote}%
    \refstepcounter{examplecounter}%
  \textbf{Example \arabic{examplecounter}}%
  \quad
}{%
%\end{quote}%
$\blacksquare$  
}

\let\OLDthebibliography\thebibliography
\renewcommand\thebibliography[1]{
  \OLDthebibliography{#1}
  \setlength{\parskip}{0pt}
  \setlength{\itemsep}{0pt plus 0.7ex}
}

@@

% RITA Preamble

\title{\pisodm: Building SOC Applications in the Presence of Non-Functional Requirements}
\author{
Khalid Belhajjame
\footnote{Universit\'e de Paris - Dauphine -- Paris, France\\
  \texttt{\{kbelhajj@googlemail.com\}}}
\and
Valeria~de~Castro
\footnote{Universidad Rey Juan Carlos -- M\'{o}stoles, Spain\\
  \texttt{\{valeria.decastro@urjc.es\}}}
\and
Umberto~Souza~da~Costa
\footnote{Universidade Federal do Rio Grande do Norte -- Natal, Brazil\\
  \texttt{\{\{umberto,mam\}@dimap.ufrn.br\}}}
\and
Javier~A.~Espinosa-Oviedo
\footnote{Universidad de las Am\'ericas-Puebla, LAFMIA -- Cholula, Mexico\
  \texttt{\{javiera.espinosa@gmail.com, joseluis.zechinelli@udlap.mx\}}}  
\and
Martin~A.~Musicante
\footnotemark[3]
\and
Pl\'acido~A.~Souza~Neto
\footnote{Instituto Federal de Educa\c{c}\~{a}o, Ci\^{e}ncia e Tecnologia do Rio Grande do Norte -- Natal, Brazil\
  \texttt{\{placido.neto@ifrn.edu.br\}}}  
\and
Genoveva~Vargas-Solar
\footnote{CNRS, LIG-LAFMIA, Saint Martin d'H\`eres, France\
  \texttt{\{genoveva.vargas@imag.fr\}}}  
\and  
Jos\'e-Luis~Zechinelli-Martini
\footnotemark[4]
}
\RITAvolume{22}
\RITAnumber{2}
\RITAyear{2015}

\begin{document}
\maketitle

%\begin{abstract}
%
%\end{abstract}

\begin{abstractinenglish}
Specifying non-functional requirements (NFRs) is a complex task, being usually dealt with on the later phases of the software process.
The late inclusion of NFRs in the development may compromise the quality of the deployed application.
This paper presents \pisodm, a method and associated tools that
\textit{(i)}  allows the early specification of NFRs in a principled way: users are abstracted away from low level details;
\textit{(ii)} embraces the MDA philosophy, generating models (code) whenever possible.
Our solution has been used in the context of an industrial and real case study.
\end{abstractinenglish}

%\keywords{MDA , Non-Functional Requirements, Service-based software process}

@@

\begin{figure*}[h]
\centering
\includegraphics[width=0.75\textwidth]{./figures/piSOD-M_process.pdf}
\caption{\pisodm Overview.}
\label{fig:piSOD-M}
\end{figure*}

>>>>

%%%%%%%%%%%%%%%%%%%%%%
\documentclass{singlecol-new}
%%%%%%%%%%%%%%%%%%%%%%

\usepackage{natbib,stfloats}
\usepackage{mathrsfs}

\def\newblock{\hskip .11em plus .33em minus .07em}

\theoremstyle{TH}{
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}[lemma]{Theorem}
\newtheorem{corrolary}[lemma]{Corrolary}
\newtheorem{conjecture}[lemma]{Conjecture}
\newtheorem{proposition}[lemma]{Proposition}
\newtheorem{claim}[lemma]{Claim}
\newtheorem{stheorem}[lemma]{Wrong Theorem}
\newtheorem{algorithm}{Algorithm}
}

\theoremstyle{THrm}{
\newtheorem{definition}{Definition}[section]
\newtheorem{question}{Question}[section]
\newtheorem{remark}{Remark}
\newtheorem{scheme}{Scheme}
\newtheorem{example}{Example}
}

\theoremstyle{THhit}{
\newtheorem{case}{Case}[section]
}

%%%% Our commands %%%%

\usepackage{xspace}
\usepackage{paralist} % for compact lists: compactitem, compactenum, compactdesc
\usepackage{graphicx}
\usepackage{subfigure}

@@

\makeatletter
\def\theequation{\arabic{equation}}

%\JOURNALNAME{\TEN{\it Int. J. System Control and Information
%Processing,
%Vol. \theVOL, No. \theISSUE, \thePUBYEAR\hfill\thepage}}%
%
%\def\BottomCatch{%
%\vskip -10pt
%\thispagestyle{empty}%
%\begin{table}[b]%
%\NINE\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcr@{}}%
%\\[-12pt]
%Copyright \copyright\ 2012 Inderscience Enterprises Ltd. & &%
%\end{tabular*}%
%\vskip -30pt%
%%%\vskip -35pt%
%\end{table}%
%}
\makeatother

%%%%%%%%%%%%%%%%%
\begin{document}%
%%%%%%%%%%%%%%%%%

\setcounter{page}{1}

\LRH{K. Belhajjame et~al.}

\RRH{\pisodm: Building SOC Applications in the Presence of Non-Functional Requirements}

\VOL{x}

\ISSUE{x}

\PUBYEAR{xxxx}

\BottomCatch

%\CLline

\PUBYEAR{2016}

\subtitle{}

\title{\pisodm: Building SOC Applications in the Presence of Non-Functional Requirements}

%
\authorA{Khalid Belhajjame}
%
\affA{Universit\'e de Paris - Dauphine -- Paris, France\\
  E-mail: kbelhajj@googlemail.com}
%
%
\authorB{Valeria~de~Castro}
\affB{Universidad Rey Juan Carlos -- M\'{o}stoles, Spain\\
  E-mail: valeria.decastro@urjc.es}
\authorC{Umberto~Souza~da~Costa}
\affC{Universidade Federal do Rio Grande do Norte -- Natal, Brazil\\
  E-mail: umberto@dimap.ufrn.br}

\authorD{Javier~A.~Espinosa-Oviedo}
\affD{Universidad de las Am\'ericas-Puebla, LAFMIA -- Cholula, Mexico\\
  E-mail: javiera.espinosa@gmail.com}

\authorE{Martin~A.~Musicante}
\affE{Universidade Federal do Rio Grande do Norte -- Natal, Brazil\\
  E-mail: mam@dimap.ufrn.br}

\authorF{Pl\'acido~A.~Souza~Neto}
\affF{Instituto Federal de Educa\c{c}\~{a}o, Ci\^{e}ncia e Tecnologia do Rio Grande do Norte -- Natal, Brazil\\
  E-mail: placido.neto@ifrn.edu.br}

\authorG{Genoveva~Vargas-Solar}
\affG{CNRS, LIG-LAFMIA, Saint Martin d'H\`eres, France\\
  E-mail: genoveva.vargas@imag.fr}

\authorH{Jos\'e-Luis~Zechinelli-Martini}
\affH{Universidad de las Am\'ericas-Puebla, LAFMIA -- Cholula, Mexico\\
  E-mail: joseluis.zechinelli@udlap.mx}

%
%\authorA{Fusheng Wang\footnote{Work done while working at Siemens Corporate Research.} }
%
%\affA{Department of Biomedical Informatics, Emory University
%\newline
%36 Eagle Row, Ste 589, Atlanta, GA 30322, USA}
%
%
%
%\authorB{\footnotesize Cristobal Vergara-Niedermayr\footnote{Work done while working at Siemens Corporate Research.}}
%\affB{Oracle \newline
 %New Jersey, USA}
%
%

\begin{abstract}
Specifying non-functional requirements (NFRs) is a complex task, being usually dealt with on the later phases of the software process.
The late inclusion of NFRs in the development may compromise the quality of the deployed application.
This paper presents \pisodm, a method and associated tools that
\textit{(i)}  allows the early specification of NFRs in a principled way: users are abstracted away from low level details;
\textit{(ii)} embraces the MDA philosophy, generating models (code) whenever possible.
Our solution has been used in the context of an industrial and real case study.
\end{abstract}

\KEYWORD{MDA , Non-Functional Requirements, Service-based software process.}

%\REF{to this paper should be made as follows: Rodr\'{\i}guez
%Bol\'{\i}var, M.P. and Sen\'{e}s Garc\'{\i}a, B. (xxxx) `The
%corporate environmental disclosures on the internet: the case of
%IBEX 35 Spanish companies', {\it International Journal of Metadata,
%Semantics and Ontologies}, Vol. x, No. x, pp.xxx\textendash xxx.}

\begin{bio}
Khalid Belhajjame\dots Bio here.

\noindent Valeria~de~Castro\dots Bio here.

\noindent Umberto~Souza~da~Costa\dots Bio here.

\noindent Javier~A.~Espinosa-Oviedo\dots Bio here.

\noindent Martin~A.~Musicante\dots Bio here.

\noindent Pl\'acido~A.~Souza~Neto\dots Bio here.

\noindent Genoveva~Vargas-Solar\dots Bio here.

\noindent Jos\'e-Luis~Zechinelli-Martini\dots Bio here.
\end{bio}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%\documentclass{RITA}
%\usepackage[T1]{fontenc}
%%\usepackage[latin1]{inputenc}
%\usepackage[english]{babel}
%
%% Our packages and definitions
%\usepackage{xspace}
%\usepackage{graphicx}
%\usepackage{paralist} % for compact lists: compactitem, compactenum, compactdesc
%\usepackage{lipsum}  % for the example environment
%\usepackage{amssymb} % for the \blacksquare symbol
%\usepackage{subfigure}
%
%\newcounter{examplecounter}
%\newenvironment{example}{%\begin{quote}%
%    \refstepcounter{examplecounter}%
%  \textbf{Example \arabic{examplecounter}}%
%  \quad
%}{%
%%\end{quote}%
%$\blacksquare$  
%}
%
%\let\OLDthebibliography\thebibliography
%\renewcommand\thebibliography[1]{
%  \OLDthebibliography{#1}
%  \setlength{\parskip}{0pt}
%  \setlength{\itemsep}{0pt plus 0.7ex}
%}
%
%\newcommand{\pisodm}[0]{$\pi$SOD-M\xspace}
%\def\FlyingPig{\textsl{FlyingPig}\xspace}
%
%% RITA Preamble
%
%\title{\pisodm: Building SOC Applications in the Presence of Non-Functional Requirements}
%\author{
%Khalid Belhajjame
%\footnote{Universit\'e de Paris - Dauphine -- Paris, France\\
%  \texttt{\{kbelhajj@googlemail.com\}}}
%\and
%Valeria~de~Castro
%\footnote{Universidad Rey Juan Carlos -- M\'{o}stoles, Spain\\
%  \texttt{\{valeria.decastro@urjc.es\}}}
%\and
%Umberto~Souza~da~Costa
%\footnote{Universidade Federal do Rio Grande do Norte -- Natal, Brazil\\
%  \texttt{\{\{umberto,mam\}@dimap.ufrn.br\}}}
%\and
%Javier~A.~Espinosa-Oviedo
%\footnote{Universidad de las Am\'ericas-Puebla, LAFMIA -- Cholula, Mexico\
%  \texttt{\{javiera.espinosa@gmail.com, joseluis.zechinelli@udlap.mx\}}}  
%\and
%Martin~A.~Musicante
%\footnotemark[3]
%\and
%Pl\'acido~A.~Souza~Neto
%\footnote{Instituto Federal de Educa\c{c}\~{a}o, Ci\^{e}ncia e Tecnologia do Rio Grande do Norte -- Natal, Brazil\
%  \texttt{\{placido.neto@ifrn.edu.br\}}}  
%\and
%Genoveva~Vargas-Solar
%\footnote{CNRS, LIG-LAFMIA, Saint Martin d'H\`eres, France\
%  \texttt{\{genoveva.vargas@imag.fr\}}}  
%\and  
%Jos\'e-Luis~Zechinelli-Martini
%\footnotemark[4]
%}
%\RITAvolume{22}
%\RITAnumber{2}
%\RITAyear{2015}
%
%\begin{document}
%\maketitle
%
%%\begin{abstract}
%%
%%\end{abstract}
%
%\begin{abstractinenglish}
%
%\end{abstractinenglish}
%
%%\keywords{}

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.75\textwidth]{./figures/piSOD-M_process.pdf}
\caption{\pisodm Overview.}
\label{fig:piSOD-M}
\end{figure}
